I don't know, are you sure you want to do this?

### 2016-10-11 submission/paper.tex
solving conflict

      <meta content="https://avatars1.githubusercontent.com/u/14945390?v=3&amp;s=400" name="twitter:image:src" /><meta content="@github" name="twitter:site" /><meta content="summary" name="twitter:card" /><meta content="eSACP/SeaLevelDecisions" name="twitter:title" /><meta content="SeaLevelDecisions - Paper on sea level change adaptation decision making under uncertainty " name="twitter:description" />
      <meta content="https://avatars1.githubusercontent.com/u/14945390?v=3&amp;s=400" property="og:image" /><meta content="GitHub" property="og:site_name" /><meta content="object" property="og:type" /><meta content="eSACP/SeaLevelDecisions" property="og:title" /><meta content="https://github.com/eSACP/SeaLevelDecisions" property="og:url" /><meta content="SeaLevelDecisions - Paper on sea level change adaptation decision making under uncertainty " property="og:description" />
      <meta name="browser-stats-url" content="https://api.github.com/_private/browser/stats">
    <meta name="browser-errors-url" content="https://api.github.com/_private/browser/errors">
    <link rel="assets" href="https://assets-cdn.github.com/">
    <link rel="web-socket" href="wss://live.github.com/_sockets/MTQ5NDUyMTM6MDUyNDYzZDIwMmVhNjNkYzMwNWI5ZWU1M2Q3NmQ3MWQ6NmY5MTBmMGJhNDA4NDZkNzQ4MGRkNDBjODdkYjBmYTI4ZjBkODAzMWJiY2IzODI3YWE5MDI3MGRjZTc0MjBkMQ==--89d25bdd8d4ae8902ca35bc19bf81c83badb6ba1">
    <meta name="pjax-timeout" content="1000">
    <link rel="sudo-modal" href="/sessions/sudo_modal">
    <meta name="request-id" content="9C740835:0C52:28EFDD9:57FCCA5A" data-pjax-transient>

@@

<meta content="collector.githubapp.com" name="octolytics-host" /><meta content="github" name="octolytics-app-id" /><meta content="9C740835:0C52:28EFDD9:57FCCA5A" name="octolytics-dimension-request_id" /><meta content="14945213" name="octolytics-actor-id" /><meta content="thordislinda" name="octolytics-actor-login" /><meta content="25d4553f8e8b0f7d5f53a85da67d6ac37df8675bf0532ac0ed5d5f1cf648984f" name="octolytics-actor-hash" />
<meta content="/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show" data-pjax-transient="true" name="analytics-location" />

@@

        <meta name="expected-hostname" content="github.com">
      <meta name="js-proxy-site-detection-payload" content="Y2ExZjFiMDljMmQxNzBiYjUzNWQzYjgxYmI2OGM1NzY0Nzc1NGRmNWJhNGVmNDNjOTJkYjc0NmJlOTA5ZGU1MXx7InJlbW90ZV9hZGRyZXNzIjoiMTU2LjExNi44LjUzIiwicmVxdWVzdF9pZCI6IjlDNzQwODM1OjBDNTI6MjhFRkREOTo1N0ZDQ0E1QSIsInRpbWVzdGFtcCI6MTQ3NjE4NDY3MX0=">

@@

  <meta content="14945390" name="octolytics-dimension-user_id" /><meta content="eSACP" name="octolytics-dimension-user_login" /><meta content="69018538" name="octolytics-dimension-repository_id" /><meta content="eSACP/SeaLevelDecisions" name="octolytics-dimension-repository_nwo" /><meta content="false" name="octolytics-dimension-repository_public" /><meta content="false" name="octolytics-dimension-repository_is_fork" /><meta content="69018538" name="octolytics-dimension-repository_network_root_id" /><meta content="eSACP/SeaLevelDecisions" name="octolytics-dimension-repository_network_root_nwo" />
  <link href="https://github.com/eSACP/SeaLevelDecisions/commits/master.atom?token=AOQLvX3BJqaD2T7TXulS-nsUHBg8-hiIks62CLlvwA%3D%3D" rel="alternate" title="Recent Commits to SeaLevelDecisions:master" type="application/atom+xml">

@@

        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/logout" class="logout-form" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="3yXD4WZhwnWJytG55fL3EwgkMSCMjYlEpuhXXi1XrsllPkR2n1RGivgoBFTGcsqjYxx3Jj0qwtsKsr9Lfl+eRQ==" /></div>
          <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout">
            Sign out
          </button>
</form>      </div>
    </div>
  </li>
</ul>

@@

  <li>
        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/notifications/subscribe" class="js-social-container" data-autosubmit="true" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="ow3eH8530MPPaY+NBuQQ2cKNOZgKM52lzUCopLpBByIcEQvPDDXmUb+PxjlwNE8m1o6yftRt4YK14tIqIWRMUQ==" /></div>      <input class="form-control" id="repository_id" name="repository_id" type="hidden" value="69018538" />

@@

    <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/unstar" class="starred" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="8jsT4FwhRy7KoSwMyDFFxWSrBfQf9q6Lff0fzQ8MdEJMZInhum5hVH/n3iXzf6+xNASq1AZqI4hBSUEtSLrMxA==" /></div>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Unstar this repository" title="Unstar eSACP/SeaLevelDecisions"
        data-ga-click="Repository, click unstar button, action:blob#show; text:Unstar">
        <svg aria-hidden="true" class="octicon octicon-star" height="16" version="1.1" viewBox="0 0 14 16" width="14"><path d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74z"></path></svg>
        Unstar
      </button>
        <a class="social-count js-social-count" href="/eSACP/SeaLevelDecisions/stargazers"
           aria-label="0 users starred this repository">
          0
        </a>
</form>
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/star" class="unstarred" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="ks2hkl+V8bZA/NAEAqFMMvvxD9L863yDs4o1AGfGlBRqFH/bqDT71HtOaVIWzDHnNEB4JjA7PZjbQqVS5B4k9w==" /></div>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Star this repository" title="Star eSACP/SeaLevelDecisions"
        data-ga-click="Repository, click star button, action:blob#show; text:Star">
        <svg aria-hidden="true" class="octicon octicon-star" height="16" version="1.1" viewBox="0 0 14 16" width="14"><path d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74z"></path></svg>
        Star
      </button>
        <a class="social-count js-social-count" href="/eSACP/SeaLevelDecisions/stargazers"
           aria-label="0 users starred this repository">
          0
        </a>
</form>  </div>

@@

          <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/branches" class="js-create-branch select-menu-item select-menu-new-item-form js-navigation-item js-new-item-form" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="DcMyzVBLpaCbk6kx2+mnhjRNC9PhE1BLNhUynTbqPElsNsRr3UzZrSuzCAJO6wgj6TKTs9w6R/B+N0T7ENYGjQ==" /></div>
          <svg aria-hidden="true" class="octicon octicon-git-branch select-menu-item-icon" height="16" version="1.1" viewBox="0 0 10 16" width="10"><path d="M10 5c0-1.11-.89-2-2-2a1.993 1.993 0 0 0-1 3.72v.3c-.02.52-.23.98-.63 1.38-.4.4-.86.61-1.38.63-.83.02-1.48.16-2 .45V4.72a1.993 1.993 0 0 0-1-3.72C.88 1 0 1.89 0 3a2 2 0 0 0 1 1.72v6.56c-.59.35-1 .99-1 1.72 0 1.11.89 2 2 2 1.11 0 2-.89 2-2 0-.53-.2-1-.53-1.36.09-.06.48-.41.59-.47.25-.11.56-.17.94-.17 1.05-.05 1.95-.45 2.75-1.25S8.95 7.77 9 6.73h-.02C9.59 6.37 10 5.73 10 5zM2 1.8c.66 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2C1.35 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2zm0 12.41c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm6-8c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"></path></svg>
            <div class="select-menu-item-text">
              <span class="select-menu-item-heading">Create branch: <span class="js-new-item-name"></span></span>
              <span class="description">from ‘master’</span>
            </div>
            <input type="hidden" name="name" id="name" class="js-new-item-value">
            <input type="hidden" name="branch" id="branch" value="master">
            <input type="hidden" name="path" id="path" value="submission/paper.tex">
</form>
      </div>

@@

        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/edit/master/submission/paper.tex" class="inline-form js-update-url-with-hash" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="JHAATQHJKo7GYe0P+sOvc4ri8m7QuFAOQBjGHnIR/IVCje5LFQxPY/7jS0hKVjDbuBVmyoHhmKRJQS4L7b7bMA==" /></div>
          <button class="btn-octicon tooltipped tooltipped-nw" type="submit"
            aria-label="Edit this file" data-hotkey="e" data-disable-with>
            <svg aria-hidden="true" class="octicon octicon-pencil" height="16" version="1.1" viewBox="0 0 14 16" width="14"><path d="M0 12v3h3l8-8-3-3-8 8zm3 2H1v-2h1v1h1v1zm10.3-9.3L12 6 9 3l1.3-1.3a.996.996 0 0 1 1.41 0l1.59 1.59c.39.39.39 1.02 0 1.41z"></path></svg>
          </button>
</form>        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/delete/master/submission/paper.tex" class="inline-form" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="GKa51xlrlUKP7iYS4nEBuU41UNrSrGU/IsCaU7p1GOZljm23SsoIOnuLz6TcbAiZmWeku1jesTDXHdkYwL0JMg==" /></div>
          <button class="btn-octicon btn-octicon-danger tooltipped tooltipped-nw" type="submit"
            aria-label="Delete this file" data-disable-with>
            <svg aria-hidden="true" class="octicon octicon-trashcan" height="16" version="1.1" viewBox="0 0 12 16" width="12"><path d="M11 2H9c0-.55-.45-1-1-1H5c-.55 0-1 .45-1 1H2c-.55 0-1 .45-1 1v1c0 .55.45 1 1 1v9c0 .55.45 1 1 1h7c.55 0 1-.45 1-1V5c.55 0 1-.45 1-1V3c0-.55-.45-1-1-1zm-1 12H3V5h1v8h1V5h1v8h1V5h1v8h1V5h1v9zm1-10H2V3h9v1z"></path></svg>
          </button>
</form>  </div>

@@

    <a href="https://github.com" aria-label="Homepage" class="site-footer-mark" title="GitHub">
      <svg aria-hidden="true" class="octicon octicon-mark-github" height="24" version="1.1" viewBox="0 0 16 16" width="24"><path d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"></path></svg>
</a>
    <ul class="site-footer-links">
      <li>&copy; 2016 <span title="0.17424s from github-fe164-cp1-prd.iad.github.net">GitHub</span>, Inc.</li>
        <li><a href="https://github.com/site/terms" data-ga-click="Footer, go to terms, text:terms">Terms</a></li>
        <li><a href="https://github.com/site/privacy" data-ga-click="Footer, go to privacy, text:privacy">Privacy</a></li>
        <li><a href="https://github.com/security" data-ga-click="Footer, go to security, text:security">Security</a></li>
        <li><a href="https://status.github.com/" data-ga-click="Footer, go to status, text:status">Status</a></li>
        <li><a href="https://help.github.com" data-ga-click="Footer, go to help, text:help">Help</a></li>
    </ul>
  </div>
</div>

>>>>

      <meta content="https://avatars1.githubusercontent.com/u/14945390?v=3&amp;s=400" name="twitter:image:src" /><meta content="@github" name="twitter:site" /><meta content="summary" name="twitter:card" /><meta content="eSACP/SeaLevelDecisions" name="twitter:title" /><meta content="SeaLevelDecisions - Paper on sea level change adaptation decision making under uncertainty " name="twitter:description" />
      <meta content="https://avatars1.githubusercontent.com/u/14945390?v=3&amp;s=400" property="og:image" /><meta content="GitHub" property="og:site_name" /><meta content="object" property="og:type" /><meta content="eSACP/SeaLevelDecisions" property="og:title" /><meta content="https://github.com/eSACP/SeaLevelDecisions" property="og:url" /><meta content="SeaLevelDecisions - Paper on sea level change adaptation decision making under uncertainty " property="og:description" />
      <meta name="browser-stats-url" content="https://api.github.com/_private/browser/stats">
    <meta name="browser-errors-url" content="https://api.github.com/_private/browser/errors">
    <link rel="assets" href="https://assets-cdn.github.com/">
    <link rel="web-socket" href="wss://live.github.com/_sockets/MTQ5NDUyMTM6MDUyNDYzZDIwMmVhNjNkYzMwNWI5ZWU1M2Q3NmQ3MWQ6OTEyMjExMTA3Zjc3ZTY5MDBmZTIyZGE3OGEzYTgzNzI0MDYwNjlmNmY5MGI1ZGZlZWUyMWI0MzQ4YWY4YjMwZA==--00f18813aa925cae31ac9371dfeeafec2e350fd1">
    <meta name="pjax-timeout" content="1000">
    <link rel="sudo-modal" href="/sessions/sudo_modal">
    <meta name="request-id" content="9C740835:0C55:4926F4F:57FCCBF1" data-pjax-transient>

@@

<meta content="collector.githubapp.com" name="octolytics-host" /><meta content="github" name="octolytics-app-id" /><meta content="9C740835:0C55:4926F4F:57FCCBF1" name="octolytics-dimension-request_id" /><meta content="14945213" name="octolytics-actor-id" /><meta content="thordislinda" name="octolytics-actor-login" /><meta content="25d4553f8e8b0f7d5f53a85da67d6ac37df8675bf0532ac0ed5d5f1cf648984f" name="octolytics-actor-hash" />
<meta content="/&lt;user-name&gt;/&lt;repo-name&gt;/blob/show" data-pjax-transient="true" name="analytics-location" />

@@

        <meta name="expected-hostname" content="github.com">
      <meta name="js-proxy-site-detection-payload" content="NmYzZGVlY2NiN2QxMTcyMGEyNWQ2YzAyZGFiMjMzODJlMmUzYTAxZmY4ZjBjYmQ0MWY2MjZlZGYzODA2Yzg5NHx7InJlbW90ZV9hZGRyZXNzIjoiMTU2LjExNi44LjUzIiwicmVxdWVzdF9pZCI6IjlDNzQwODM1OjBDNTU6NDkyNkY0Rjo1N0ZDQ0JGMSIsInRpbWVzdGFtcCI6MTQ3NjE4NTA3NH0=">

@@

  <meta content="14945390" name="octolytics-dimension-user_id" /><meta content="eSACP" name="octolytics-dimension-user_login" /><meta content="69018538" name="octolytics-dimension-repository_id" /><meta content="eSACP/SeaLevelDecisions" name="octolytics-dimension-repository_nwo" /><meta content="false" name="octolytics-dimension-repository_public" /><meta content="false" name="octolytics-dimension-repository_is_fork" /><meta content="69018538" name="octolytics-dimension-repository_network_root_id" /><meta content="eSACP/SeaLevelDecisions" name="octolytics-dimension-repository_network_root_nwo" />
  <link href="https://github.com/eSACP/SeaLevelDecisions/commits/master.atom?token=AOQLvTof4iBfdh_bxi-mAYExYzZraD1Yks62CLsCwA%3D%3D" rel="alternate" title="Recent Commits to SeaLevelDecisions:master" type="application/atom+xml">

@@

        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/logout" class="logout-form" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="g3xzxmHvQyOZcdduEA2nIbMpdP5YMK990mQfSMu9pM1TjktF+qOiz6MsCcmnYQ+Jt1cPiz7zttHuxK0uLsGXCQ==" /></div>
          <button type="submit" class="dropdown-item dropdown-signout" data-ga-click="Header, sign out, icon:logout">
            Sign out
          </button>
</form>      </div>
    </div>
  </li>
</ul>

@@

  <li>
        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/notifications/subscribe" class="js-social-container" data-autosubmit="true" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="hNtXU+QFowQO8xu8ntiXO7r1xdu0xBY4GIIFLQWB7Y6JYx/XEVgXHLnlsLMxDCsUXDu3vdNe3hrVOf/ZCR7rYQ==" /></div>      <input class="form-control" id="repository_id" name="repository_id" type="hidden" value="69018538" />

@@

    <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/unstar" class="starred" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="GtlnpB914Jk1PD4m5DjZFtsdzJjGqKhfPlnTw/rmDmISrKiyNaWrqDj4fIZ3t1Dfm8u/tXyRQe1rb3gYakhOow==" /></div>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Unstar this repository" title="Unstar eSACP/SeaLevelDecisions"
        data-ga-click="Repository, click unstar button, action:blob#show; text:Unstar">
        <svg aria-hidden="true" class="octicon octicon-star" height="16" version="1.1" viewBox="0 0 14 16" width="14"><path d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74z"></path></svg>
        Unstar
      </button>
        <a class="social-count js-social-count" href="/eSACP/SeaLevelDecisions/stargazers"
           aria-label="0 users starred this repository">
          0
        </a>
</form>
    <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/star" class="unstarred" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="JTg/qUMW8crgT/1Wxronr7Df4zFgXi4/AcBQdn4HM8g9fuZv6zWaC+roC7DS+jxfKAkNyyzVbwM1Tmr974bDCg==" /></div>
      <button
        type="submit"
        class="btn btn-sm btn-with-count js-toggler-target"
        aria-label="Star this repository" title="Star eSACP/SeaLevelDecisions"
        data-ga-click="Repository, click star button, action:blob#show; text:Star">
        <svg aria-hidden="true" class="octicon octicon-star" height="16" version="1.1" viewBox="0 0 14 16" width="14"><path d="M14 6l-4.9-.64L7 1 4.9 5.36 0 6l3.6 3.26L2.67 14 7 11.67 11.33 14l-.93-4.74z"></path></svg>
        Star
      </button>
        <a class="social-count js-social-count" href="/eSACP/SeaLevelDecisions/stargazers"
           aria-label="0 users starred this repository">
          0
        </a>
</form>  </div>

@@

          <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/branches" class="js-create-branch select-menu-item select-menu-new-item-form js-navigation-item js-new-item-form" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="tFLJXyMYF5qjVGsC1skVetROtxEq1jGt+I7qMaqTbXk4eX+2eWczuOKNAgbqOkMj6YkPiqcTebby8Fc6dw9Mug==" /></div>
          <svg aria-hidden="true" class="octicon octicon-git-branch select-menu-item-icon" height="16" version="1.1" viewBox="0 0 10 16" width="10"><path d="M10 5c0-1.11-.89-2-2-2a1.993 1.993 0 0 0-1 3.72v.3c-.02.52-.23.98-.63 1.38-.4.4-.86.61-1.38.63-.83.02-1.48.16-2 .45V4.72a1.993 1.993 0 0 0-1-3.72C.88 1 0 1.89 0 3a2 2 0 0 0 1 1.72v6.56c-.59.35-1 .99-1 1.72 0 1.11.89 2 2 2 1.11 0 2-.89 2-2 0-.53-.2-1-.53-1.36.09-.06.48-.41.59-.47.25-.11.56-.17.94-.17 1.05-.05 1.95-.45 2.75-1.25S8.95 7.77 9 6.73h-.02C9.59 6.37 10 5.73 10 5zM2 1.8c.66 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2C1.35 4.2.8 3.65.8 3c0-.65.55-1.2 1.2-1.2zm0 12.41c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2zm6-8c-.66 0-1.2-.55-1.2-1.2 0-.65.55-1.2 1.2-1.2.65 0 1.2.55 1.2 1.2 0 .65-.55 1.2-1.2 1.2z"></path></svg>
            <div class="select-menu-item-text">
              <span class="select-menu-item-heading">Create branch: <span class="js-new-item-name"></span></span>
              <span class="description">from ‘master’</span>
            </div>
            <input type="hidden" name="name" id="name" class="js-new-item-value">
            <input type="hidden" name="branch" id="branch" value="master">
            <input type="hidden" name="path" id="path" value="submission/paper.tex">
</form>
      </div>

@@

        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/edit/master/submission/paper.tex" class="inline-form js-update-url-with-hash" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="sjcXEW9oK9etoucE/sg8MOSNquWSXWvPhhM/jB58oJiS7Gk4B62bRn8/K6+aSzGHLvp8q3NHn/DV+c8Z9zqmBw==" /></div>
          <button class="btn-octicon tooltipped tooltipped-nw" type="submit"
            aria-label="Edit this file" data-hotkey="e" data-disable-with>
            <svg aria-hidden="true" class="octicon octicon-pencil" height="16" version="1.1" viewBox="0 0 14 16" width="14"><path d="M0 12v3h3l8-8-3-3-8 8zm3 2H1v-2h1v1h1v1zm10.3-9.3L12 6 9 3l1.3-1.3a.996.996 0 0 1 1.41 0l1.59 1.59c.39.39.39 1.02 0 1.41z"></path></svg>
          </button>
</form>        <!-- '"` --><!-- </textarea></xmp> --></option></form><form accept-charset="UTF-8" action="/eSACP/SeaLevelDecisions/delete/master/submission/paper.tex" class="inline-form" data-form-nonce="01c9606cf95d90aee2e58783cb1f27d1662fa6a0" method="post"><div style="margin:0;padding:0;display:inline"><input name="utf8" type="hidden" value="&#x2713;" /><input name="authenticity_token" type="hidden" value="UohHCkSZS8wL4Q+ZfdepYV6n/fcmZBwa9J2ho7rJyhhMkr0x3hgPcbMUhMl9KEoLHk0YZZgNoF3pja5PRrYVVg==" /></div>
          <button class="btn-octicon btn-octicon-danger tooltipped tooltipped-nw" type="submit"
            aria-label="Delete this file" data-disable-with>
            <svg aria-hidden="true" class="octicon octicon-trashcan" height="16" version="1.1" viewBox="0 0 12 16" width="12"><path d="M11 2H9c0-.55-.45-1-1-1H5c-.55 0-1 .45-1 1H2c-.55 0-1 .45-1 1v1c0 .55.45 1 1 1v9c0 .55.45 1 1 1h7c.55 0 1-.45 1-1V5c.55 0 1-.45 1-1V3c0-.55-.45-1-1-1zm-1 12H3V5h1v8h1V5h1v8h1V5h1v8h1V5h1v9zm1-10H2V3h9v1z"></path></svg>
          </button>
</form>  </div>

@@

    <a href="https://github.com" aria-label="Homepage" class="site-footer-mark" title="GitHub">
      <svg aria-hidden="true" class="octicon octicon-mark-github" height="24" version="1.1" viewBox="0 0 16 16" width="24"><path d="M8 0C3.58 0 0 3.58 0 8c0 3.54 2.29 6.53 5.47 7.59.4.07.55-.17.55-.38 0-.19-.01-.82-.01-1.49-2.01.37-2.53-.49-2.69-.94-.09-.23-.48-.94-.82-1.13-.28-.15-.68-.52-.01-.53.63-.01 1.08.58 1.23.82.72 1.21 1.87.87 2.33.66.07-.52.28-.87.51-1.07-1.78-.2-3.64-.89-3.64-3.95 0-.87.31-1.59.82-2.15-.08-.2-.36-1.02.08-2.12 0 0 .67-.21 2.2.82.64-.18 1.32-.27 2-.27.68 0 1.36.09 2 .27 1.53-1.04 2.2-.82 2.2-.82.44 1.1.16 1.92.08 2.12.51.56.82 1.27.82 2.15 0 3.07-1.87 3.75-3.65 3.95.29.25.54.73.54 1.48 0 1.07-.01 1.93-.01 2.2 0 .21.15.46.55.38A8.013 8.013 0 0 0 16 8c0-4.42-3.58-8-8-8z"></path></svg>
</a>
    <ul class="site-footer-links">
      <li>&copy; 2016 <span title="0.12379s from github-fe162-cp1-prd.iad.github.net">GitHub</span>, Inc.</li>
        <li><a href="https://github.com/site/terms" data-ga-click="Footer, go to terms, text:terms">Terms</a></li>
        <li><a href="https://github.com/site/privacy" data-ga-click="Footer, go to privacy, text:privacy">Privacy</a></li>
        <li><a href="https://github.com/security" data-ga-click="Footer, go to security, text:security">Security</a></li>
        <li><a href="https://status.github.com/" data-ga-click="Footer, go to status, text:status">Status</a></li>
        <li><a href="https://help.github.com" data-ga-click="Footer, go to help, text:help">Help</a></li>
    </ul>
  </div>
</div>
